### 2022-08-12 README.Rmd
Updated description and licensing information

<!-- badges: start -->
[![License: CC BY-NC-SA 4.0](https://img.shields.io/badge/license-CC BY--NC--SA 4.0-blue.svg)](https://creativecommons.org/licenses/by-nc-sa/4.0/deed.en_GB)

>>>>

<!-- badges: start -->
[![License: CC BY-NC-SA 4.0](https://img.shields.io/badge/license-ODbLv1.0-blue.svg)](https://opendatacommons.org/licenses/odbl/1-0/)
